The expected shape of the Milky Way's Dark Matter halo

### 2019-02-13 Paper/paper.tex
edit

\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}

@@

We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
function of radius. 
As a representative sample of this
relations, we show on figure \ref{fig:triaxial_radius} the evolution, for
a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile} \label{fig:triaxial_radius}
\end{figure}

>>>>

\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\kpch}{\,{\rm kpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\kpc}{\,{\rm kpc}\,}

@@

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/halo16.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile} \label{fig:triaxial_radius}
\end{figure*}

We quantify this effect by plotting the axial ratios $q$, $s$,
$s/q$ and the triaxiality $T\equiv \frac{1-q}{1-s}$ as a
function of radius. 
As a representative sample of this relations we show on Figure
\ref{fig:triaxial_radius} the radial trends for Halo 16 at
the highest resolution both for DM and MHD simulations.
The continous lines correspond to the DM simulation and shows how
the inner part of the halo $r\approx 1$\kpch has values of 
$q=0.5$, $s=0.5$ while at the virial radius the same
quantities increase to $q=0.85$, $s=0.6$; in turn the triaxiality
decreases from $T\approx 1.0$ to $T\approx0.4$.

In the same Figure \ref{fig:triaxial_radius} we also find one of the
main results of our study: halos in MHD simulations are systematically rounder, at
every radius, than its DM-only counterparts.  
The dashed line in Figure \ref{fig:triaxial_radius} shows that at
$r\approx 1$\kpch  in the MHD simulation we have $q=0.85, s=0.8$
($q=0.5, s=0.5$ in DM) and at the virial radius $q=0.95, s=0.75$
($q=0.85, s=0.6$ in DM).  
However, the triaxiality trend is not as monotonous for MHD halos is
it is in DM halos. 
The triaxiality goes almost to zero at an intermediate radius,
$r\approx 10$\kpc in the case of Halo 16 in Figure
\ref{fig:triaxial_radius}, to increase again. {\bf pasa lo mismo para
  todos los halos? es lo mismo para baja y alta resolucion de MHD?}
